Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-20 latex/article.tex
minor

\begin{Definition}
  %
  Given $\DigShape \subset \Z^2$ (or $\Z^3$ for 3D mean curvature estimator) and
  $h$ a gridstep, {\em digital curvature estimators} are defined for any pointel
  $\vp \in \Body{\DigShape}{h}$ as:
  %
  \begin{align}
   \CurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{3 \pi}{2 R_d} - \frac{3 A_{R_d}(\vp)}{{R_d}^3} \right),\label{eq:dig-curvature-estimator-k}\\
   \MeanCurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{8}{3 R_d} - \frac{4V_{R_d}(\vp)}{{\pi R_d}^4} \right),\label{eq:dig-curvature-estimator-H}
  %  \\
  %  \hat{\kappa}^{1}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_2 - 3\hat{\lambda}_1)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),\label{eq:dig-curvature-estimator-k1}\\
  %  \hat{\kappa}^{2}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_1 - 3\hat{\lambda}_2)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),
  %  \label{eq:dig-curvature-estimator-k2}
  \end{align}
  %
  where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
  $A_{R_d}(p)$ and $V_{R_d}(p)$ are the number of digital points in the
  intersection between $\DigShape$ and the ball.
  % Similarly, $\hat{\lambda}_1$
  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
  % matrix of the digital points in the intersection between $Z$ and the ball.
  %
\end{Definition}

>>>>

\begin{Definition}
  %
  Given $\DigShape \subset \Z^2$ (or $\Z^3$ for 3D mean curvature estimator) and
  $h$ a gridstep, {\em digital curvature estimators} are defined for any pointel
  $\vp \in \Body{\DigShape}{h}$ as:
  %
  \begin{align}
   \CurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{3 \pi}{2 R_d} - \frac{3 A_{R_d}(\vp)}{{R_d}^3} \right),\label{eq:dig-curvature-estimator-k}\\
   \MeanCurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{8}{3 R_d} - \frac{4V_{R_d}(\vp)}{{\pi R_d}^4} \right),\label{eq:dig-curvature-estimator-H}
  %  \\
  %  \hat{\kappa}^{1}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_2 - 3\hat{\lambda}_1)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),\label{eq:dig-curvature-estimator-k1}\\
  %  \hat{\kappa}^{2}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_1 - 3\hat{\lambda}_2)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),
  %  \label{eq:dig-curvature-estimator-k2}
  \end{align}
  %
  where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
  $A_{R_d}(p)$ and $V_{R_d}(p)$ are the number of digital points in the
  intersection between $\DigShape$ and the ball, $\DigShape\cap B_{R_d}(\vp)$.
  % Similarly, $\hat{\lambda}_1$
  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
  % matrix of the digital points in the intersection between $Z$ and the ball.
  %
\end{Definition}
